### 2021-04-17 manuscript.rmd
small edits

Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120]. However, for Bayesian models priors have to be chosen by researchers.

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. More often than not, we do not have any information to set an informative prior (e.g. What about a new journal?). One option is to consult experts or to make an educated guess. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

@@

A dictionary-based approach was used. The seed English and German dictionaries from the R package newsmap [@watanabe:2017:N] were used as the basis. The seed dictionaries contain words about Chinese, China, Beijing and Shanghai. We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries. The dictionaries were applied to the 61 DTMs of all included media outlets. An article is classified as China coverage when at least one dictionary match is detected.

@@

For all analyses, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression. It is important to remind our readers that the results from the three are likely to be similar, but it is not an evidence for the disaggregation approach and the MLE approach are replacement of Bayesian approach. It is because disaggregation approach commits atomistic fallacy and MLE approach ignores the non-stochastic nature of the data.

@@

Consistently, point estimates are remarkably similar. Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods. It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF]. The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China. While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference. The Bayesian approach allows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling within  0.18 and 0.33*. In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*. One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way [@morey:2015]. This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.

>>>>

Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120]. However, for Bayesian models so-called priors have to be chosen by researchers.

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. More often than not, we do not have any information to set an informative prior (e.g. What about a new journal for which no acceptance rate is yet known?). One option is to consult experts or to make an educated guess. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

@@

A dictionary-based approach was used. The seed English and German dictionaries from the R package newsmap [@watanabe:2017:N] were used as the basis. The seed dictionaries contain words about Chinese, China, Beijing and Shanghai. We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries. The dictionaries were applied to the 61 document-term matrices (format of the provided dataset) of all included media outlets. An article is classified as China coverage when at least one dictionary match is detected.

@@

For all analyses, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression. It is important to remind our readers that the results from the three are likely to be similar, but it is not an evidence for the disaggregation approach and the MLE approach are replacement of Bayesian approach [@morey:2015]. It is because disaggregation approach commits atomistic fallacy and MLE approach ignores the non-stochastic nature of the data.

@@

Consistently, point estimates are remarkably similar. Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods. It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF]. The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China. While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference. The Bayesian approach allows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling within  0.18 and 0.33*. In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*. One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way as described above [@morey:2015]. This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.
